---
title: "Cut&Run QC Report"
author: "Andrew Clugston"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    code_folding: hide
params:
  ctrl_epitope: "IgG"
  out_dir: "/N/p/asclab/ASC-cutNrun/nextflow_v2/data_100000"
---

```{r setup, include=FALSE}
library(tidyverse)
library(data.table)
library(clugPac)
library(ggplot2)
library(magrittr)
library(scales)
library(knitr)
library(kableExtra)
library(cowplot)
library(GenomicRanges)
library(ggnewscale)
library(DT)
library(ggrepel)

# Aliases.
mutate  <- dplyr::mutate
filter  <- dplyr::filter
arrange <- dplyr::arrange
rename  <- dplyr::rename

# Source functions.
sapply(Sys.glob("R_functions/*.R"),source)

knitr::opts_chunk$set(echo = FALSE,warning = FALSE,message = FALSE)
# For debugging, set stage directory here.
# setwd("/N/p/asclab/ASC-cutNrun/nextflow_v2/work/bb/2d9f4ddebcafc045cb198be36d852a")
```

```{r loadData}
extract_rep_name  <- function(txt_in="alignment_prime/OS457_IgG_NONE_1_hg38_alignment_report.txt"){
  str_extract(basename(txt_in),"^([:alnum:]+_[:alnum:]+_[:alnum:]+_[:digit:]+_)") %>%
    gsub("_$","",.)
}
extract_pool_name <- function(txt_in="narrowPeaks_pool/OS457_K27Ac_NONE_control_lambda.bdg.gz"){
  str_extract(basename(txt_in),"^([:alnum:]+_[:alnum:]+_[:alnum:]+)")
}
read_spike_frac   <- function(fl_nm="assignment/OS457_IgG_NONE_2_spike.tsv"){
  vals <- fread(fl_nm,sep="\t") %>%
    as_tibble %>%
    mutate(V1=case_when(row_number() == 1 ~ "primary",
                        row_number() == 2 ~ "spike",
                        TRUE ~ V1)) %>%
    vectify(V2,V1)
  return(vals[['spike']]/(vals[['spike']]+vals[['primary']]))
}
read_pct_alignment  <- function(fl_nm="/N/p/asclab/ASC-cutNrun/nextflow_v2/work/bb/2d9f4ddebcafc045cb198be36d852a/reps/align/OS457_IgG_NONE_1_spike.tsv"){
  vals <- fread(fl_nm,sep="\t") %>%
    as_tibble %>%
    mutate(V1=case_when(row_number() == 1 ~ "primary",
                        row_number() == 2 ~ "spike",
                        TRUE ~ V1)) %>%
    vectify(V2,V1)
  return((vals[['spike']] + vals[['primary']])/sum(vals))
}
read_frip_score     <- function(fl_nm="reps/qc/OS457_K4Me3_NONE_2_narrowPeaks_FRiP.txt"){
  return(fread(fl_nm)$frip)
}
gn_gtf <- file.path("genes.gtf")
tb_input  <- fread("file_table.csv") %>%
  as_tibble %>%
  mutate(rep_name=paste(cell_line,epitope,cond,rep,sep="_")) %>%
  rename(input_R1=R1,input_R2=R2)

lst_files <- tibble(path=dir(recursive=TRUE)) %>%
  mutate(dir = dirname(path),
         dir = ifelse(dir == ".","base",dir)) %>%
  filter(!dir %in% c("base","R_functions")) %>%
  mutate(rep_name = extract_rep_name(path),
         pool_name = extract_pool_name(path),
         set= ifelse(is.na(rep_name),"pool","rep"),
         name=ifelse(set == "rep",rep_name,pool_name)) %>%
  select(-rep_name,-pool_name) %>%
  group_split(dir) %>%
  setNames(sapply(.,function(x) gsub("/","_",x$dir[1])))


# Replicates.
tb_peaks  <- lst_files$reps_peaks %>%
  filter(!grepl(".tbi$",path)) %>%
  mutate(type = str_match(basename(path),paste0(name,"_([[:alnum:]_]+)\\.*"))[,2]) %>%
  mutate(type = case_when(grepl("broadPeak$",path) ~ "bpks",
                          grepl("narrowPeak$",path) ~ "npks",
                          type == "summit_regions" ~ "summits",
                          type == "treat_pileup" ~ "bdg",
                          type == "control_lambda" ~ "bdg_ctrl",
                          TRUE ~ type)) %>%
  pivot_wider(id_cols = name,values_from = path,names_from = type) %>%
  select(name,npks,bpks,summits,bdg,bdg_ctrl)

tb_align  <- lst_files$reps_align %>%
  mutate(type = case_when(grepl("_spike.tsv$",path)~"spike",
                          grepl("_short.bam$",path) ~ "bam",
                          TRUE ~ "other")) %>%
  filter(type != "other") %>%
  pivot_wider(id_cols = name,values_from = path,names_from = type)

tb_qc   <- lst_files$reps_qc %>%
  mutate(type = str_match(basename(path),paste0(name,"_([[:alnum:]_]+)\\.*"))[,2]) %>%
  mutate(type = gsub("broadPeaks","bpks",type),
         type = gsub("narrowPeaks","npks",type),
         type = gsub("report","rpt",type),
         type = case_when(type == "val_1_fastqc" ~ "fqc_r1_trim",
                          type == "val_2_fastqc" ~ "fqc_r2_trim",
                          grepl("_short_fastqc",type) ~ "fqc_filt",
                          TRUE ~ type)) %>%
  pivot_wider(id_cols = name,values_from = path,names_from = type)

tb_reps   <- fread("reps.csv",sep=",",header=FALSE,
                   col.names=c("project","name","cell_line","epitope","cond","rep","rep_name","pool_name","rep_dir","pool_dir","genome","genome_spike")) %>%
  as_tibble %>%
  select(-name,-genome,-genome_spike) %>%
  mutate_at(c("cell_line","epitope","cond"),factor) %>%
  arrange(cell_line,epitope,cond) %>%
  left_join(tb_input,by=c("project","rep_name","cell_line","epitope","cond","rep")) %>%
  left_join(tb_peaks,by=c("rep_name"="name")) %>%
  left_join(tb_align,by=c("rep_name"="name")) %>%
  left_join(tb_qc,by=c("rep_name"="name")) %>%
  rename(spike_file=spike) %>%
  rowwise %>%
  mutate(spike = read_spike_frac(spike_file),
         pct_alignment = read_pct_alignment(spike_file),
         frip = read_frip_score(npks_FRiP)) %>%
  ungroup %>%
  mutate(bkg = epitope == params$ctrl_epitope,
         pool_name = ifelse(bkg,NA,pool_name),
         pool_dir = ifelse(bkg,NA,pool_dir))

tb_reps_output <- tb_reps %>%
  rowwise %>%
  mutate(across(-rep_dir, ~ gsub("^reps",rep_dir,.))) %>%
  ungroup %T>%
    fwrite(paste0(tb_reps$project[1],"_replicates.tsv"),sep="\t",row.names=FALSE,col.names=TRUE,quote=FALSE)

# Pooled
tb_align  <- lst_files$pool_align %>%
  mutate(type = str_match(basename(path),paste0(name,"_([[:alnum:]_]+)\\.*"))[,2]) %>%
  filter(type == "spike") %>%
  pivot_wider(id_cols = name,names_from = type,values_from=path)

tb_peaks  <- lst_files$pool_peaks %>%
  filter(!grepl(".tbi$",path)) %>%
  mutate(type = str_match(basename(path),paste0(name,"_([[:alnum:]_]+)\\.*"))[,2]) %>%
  mutate(type = case_when(grepl("narrowPeak$",path) ~ "npks",
                          grepl("broadPeak$",path) ~ "bpks",
                          type == "control_lambda" ~ "bdg_ctrl",
                          type == "treat_pileup" ~ "bdg",
                          type == "summit_regions" ~ "summits",
                          TRUE ~ type)) %>%
  pivot_wider(id_cols = name,values_from = path,names_from = type) %>%
  select(name,npks,bpks,summits,bdg,bdg_ctrl)

tb_qc <- lst_files$pool_qc %>%
  mutate(type = str_match(basename(path),paste0(name,"_([[:alnum:]_]+)\\.*"))[,2]) %>% 
  mutate(type = gsub("broadPeaks","bpks",type),
         type = gsub("narrowPeaks","npks",type),
         type = gsub("report","rpt",type)) %>%
  pivot_wider(id_cols = name,values_from = path,names_from = type)

tb_pool   <- fread("pools.csv",sep=",",header=FALSE,
                   col.names=c("project","pool_name","cell_line","epitope","cond","reps","reps_bkg","pool_dir","genome","genome_spike","bams","bams_bkg")) %>%
  as_tibble %>%
  select(-bams,-bams_bkg) %>%
  mutate_at(c("cell_line","epitope","cond"),factor) %>%
  arrange(cell_line,epitope,cond) %>%
  left_join(tb_align,by=c("pool_name"="name")) %>%
  left_join(tb_peaks,by=c("pool_name"="name")) %>%
  left_join(tb_qc, by = c("pool_name"="name")) %>%
  rename(spike_file=spike) %>%
  rowwise %>%
  mutate(spike = read_spike_frac(spike_file)) %>%
  ungroup

rm(tb_peaks);rm(tb_qc);rm(tb_align)

tb_pool_output <- tb_pool %>%
  rowwise %>%
  mutate(across(-pool_dir, ~ gsub("^pool",pool_dir,.))) %>%
  ungroup %T>%
    fwrite(paste0(tb_pool$project[1],"_pools.tsv"),sep="\t",row.names=FALSE,col.names=TRUE,quote=FALSE)

ep_colors <- unique(as.character(tb_reps$epitope)) %>% setdiff(params$ctrl_epitope)
ep_colors <- c(setNames(hue_pal()(length(ep_colors)),ep_colors),setNames("#a6a6a6",params$ctrl_epitope))
```

# Files {.tabset}
## Pools
```{r tablePools}
tb_pool_output %>%
  rowwise %>%
  mutate(across(c(reps,reps_bkg), ~ gsub(":","\n",.))) %>%
  DT::datatable(class = "cell-border stripe",
                rownames=FALSE,
                filter="top",
                editable=FALSE,
                extensions="Buttons",
                options = list(dom="Bfrtip",buttons = c("copy","csv","excel","pdf","print")))
```

## Replicates
```{r tableReps}
DT::datatable(tb_reps_output,
              class = 'cell-border stripe',
              rownames=FALSE,
              filter="top",
              editable=FALSE,
              extensions="Buttons",
              options = list(dom="Bfrtip",buttons = c("copy","csv","excel","pdf","print")))
```

# FastQC
## Raw FastQ files {.tabset}
```{r fastqcRead}
tb_fls  <- select(tb_reps,rep_name,starts_with("fqc"),trim_rpt)

fq_raw1 <- clugPac::read_fastqc(tb_fls$fqc_r1_trim)
fq_raw2 <- clugPac::read_fastqc(tb_fls$fqc_r2_trim)

fq_raw  <- lapply(names(fq_raw1), function(nm){
  tb1   <- fq_raw1[[nm]]
  tb2   <- fq_raw2[[nm]]
  
  if(!is.null(tb1)){
    tb1 <- mutate(tb1,read="R1")
  }
  if(!is.null(tb2)){
    tb2 <- mutate(tb2,read="R2")
  }
  if(!is.null(tb1) & !is.null(tb2)){
    tb <- rbind(tb1,tb2)
  }else if(!is.null(tb1)){
    tb <- tb1
  }else if(is.null(tb2)){
    tb <- tb2
  }else{
    tb <- NULL
  }
  return(as_tibble(tb))
}) %>% setNames(names(fq_raw1))
```

### Flag summary
```{r fastqcSummary}
p_file <- "fastqc_flags.png"
if(is.null(fq_raw$summary)){
  p <- ggplot() + theme_void()
  p_height<- 1
  p_width <- 1
}else{
  tb_p  <- fq_raw$summary %>%
    mutate(name = gsub("_val_[12]$","",name)) %>%
    separate(name,into=c("cell_line","epitope","cond","rep"),sep = "_",remove = FALSE) %>%
    mutate(cell_line = factor(cell_line),
           epitope = factor(epitope),
           cond = factor(cond),
           read = factor(read),
           rep = factor(rep),
           flag = factor(flag,levels=c("pass","warn","fail")),
           title = factor(title),
           idx = row_number()) %>%
    rowwise %>%
    mutate(x = ifelse(read == "R1",list(c(0,1,0)),list(c(0,1,1))),
           y = ifelse(read == "R1",list(c(1,1,0)),list(c(0,1,0)))) %>%
    ungroup %>%
    unnest(c(x,y)) %>%
    mutate(x = x + (as.integer(rep)-1),
           y = y + (as.integer(title)-1))
  
  y_labs  <- levels(tb_p$title)
  y_labs  <- setNames(c(1:length(y_labs))-0.5,y_labs)
  x_labs  <- levels(tb_p$rep)
  x_labs  <- setNames(c(1:length(x_labs))-0.5,x_labs)
  p <- ggplot(tb_p,aes(x=x,y=y,group=idx,fill=flag)) +
    facet_wrap(.~cell_line+epitope+cond,nrow=1,scales = "free_x") +
    scale_x_continuous(name = "Replicate",
                       expand=c(0,0),
                       breaks=x_labs,
                       labels = names(x_labs)) +
    scale_y_reverse(expand=c(0,0),
                       breaks = y_labs,
                       labels = names(y_labs))+
    scale_fill_manual(values=c(pass="lightgreen",
                               warn="orange",
                               fail="firebrick")) +
    geom_polygon(color="black") +
    annotate(geom = "text",x=0.05,y=0.95,hjust=0,vjust=0,label="R1",size=2.5) +
    annotate(geom = "text",x=0.95,y=0.05,hjust=1,vjust=1,label="R2",size=2.5) +
    ggtitle("Raw reads") +
    theme_minimal() +
    theme(plot.title = element_text(size=7),
          plot.background= element_rect(fill="white",color=NA),
          axis.text = element_text(size=4),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          axis.title.y = element_blank(),
          legend.title = element_blank(),
          legend.text = element_text(size=5),
          legend.key.height = unit(0.5,"lines"),
          legend.key.width = unit(0.5,"lines"),
          strip.text = element_text(size=5))
  n_cols <- tb_p %>% select(cell_line,epitope,cond) %>% distinct %>% nrow
  p_height  <- 4
  p_width   <- 1+0.7*n_cols
}
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### FastQ Reads {.tabset}
```{r tableStats}
tb_stats <- fq_raw$basic_statistics %>%
  filter(read == "R1") %>%
  mutate(name = gsub("_val_1","",name),
         measure = gsub(" ","_",gsub("%","pct_",tolower(measure)))) %>%
  pivot_wider(id_cols = name,
              names_from = measure,
              values_from = value) %>%
  select(name,total_sequences,total_bases,sequence_length,pct_gc) %>%
  mutate(total_sequences = as.double(total_sequences)) %>%
  rename(rep_name=name) %>%
  left_join(by="rep_name",
    select(tb_reps,rep_name,cell_line,epitope,cond,rep)) %>%
  arrange(cell_line,epitope,cond) %>%
  mutate(rep_name = factor(rep_name,levels=select(.,rep_name) %>% unlist %>% unique)) %>%
  select(cell_line,epitope,cond,rep,everything())
```

#### Barplot
```{r plotFastqReads}
p_file <- "fastqc_barplot_reads.png"
p <- ggplot(tb_stats,aes(x=rep_name,y=total_sequences,fill=epitope,label=paste0(prettyNumbers(total_sequences,digs = 1),"\n"))) +
  facet_wrap(.~cell_line+cond,scales="free_x",nrow=1) +
  scale_y_continuous(labels = prettyNumbers,name="Reads",expand=expansion(mult=c(0,0.1))) +
  scale_fill_manual(values=ep_colors) +
  geom_bar(stat='identity',position = "dodge",color='black',linewidth=0.5) +
  geom_text(size=2) +
  ggtitle("FastQ read counts",subtitle= "Unfiltered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height=unit(0.5,"lines"),
        legend.key.width=unit(0.5,"lines"),
        axis.text.x = element_text(angle=45,hjust=1,vjust=1,size=5),
        axis.ticks.x = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size=6),
        axis.title.x = element_blank())
n_col <- length(unique(tb_stats$rep_name))
p_height<- 4
p_width <- 1+n_col*0.4
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

#### Table
```{r fastqStatsTable}
tb_stats %>%
  mutate(total_sequences = prettyNumbers(total_sequences)) %>%
  kable %>%
  kable_styling(full_width=FALSE)
```

### Per-base quality scores
```{r plotPerBaseSequenceQuality}
p_file <- "fastqc_pb_sequence_quality.png"
tb_p <- fq_raw$per_base_sequence_quality %>%
  mutate(base = ifelse(read == "R2",-base,base),
         name = gsub("_val_[12]$","",name))

p <- ggplot(tb_p,aes(x=base,y=mean,color=name)) +
  facet_wrap(.~read,nrow=1,scales="free_x") +
  scale_x_continuous(name="Base (bp)",expand=c(0,0),labels=abs) + 
  scale_y_continuous(name="Quality score") +
  geom_line() +
  ggtitle("Per-base quality scores",subtitle= "Unfiltered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        axis.ticks.x = element_blank(),
        strip.background = element_blank())
p_height  <- 4
p_width   <- 10
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### Per-base sequence content
```{r perBaseSequenceContent}
p_file  <- "fastqc_pb_sequence_content.png"
tb_p <- fq_raw$per_base_sequence_content %>%
  mutate(rep_name = gsub("_val_[12]$","",name),
         base = ifelse(read == "R2",-base,base)) %>%
  as_tibble %>%
  left_join(select(tb_reps,rep_name,cell_line,epitope,cond,rep),by="rep_name") %>%
  mutate(cond = paste(cell_line,rep)) %>%
  rename(position = base) %>%
  pivot_longer(cols=c(a,c,g,t),names_to = "base",values_to="percent")

p <- ggplot(tb_p,aes(x=position,y=percent,color=cond,linetype=base)) +
  facet_grid(rows=vars(epitope),cols=vars(read),scales="free_x") +
  scale_x_continuous(name="Base",expand=c(0,0),labels=abs) +
  scale_y_continuous(name="Percent",labels = function(x) paste0(x,"%")) +
  geom_line() +
  ggtitle("Per-base sequence content",subtitle="Unfiltered") +
  theme(plot.background = element_rect(fill="white",color=NA),
          plot.subtitle = element_text(face="italic"),
          panel.background = element_blank(),
          panel.border = element_rect(fill = NA,color='black'),
          panel.grid.major.x = element_blank(),
          panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
          legend.title = element_blank(),
          axis.ticks.x = element_blank(),
          strip.background = element_blank())
n_row <- length(unique(tb_p$epitope))
p_height  <- 1+n_row*1.1
p_width   <- 8
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### Per-sequence GC content
```{r perSequenceGCContent,fig.height=6,fig.width=8}
p_file<- "fastqc_ps_gc_content.png"
tb_p  <- fq_raw$per_sequence_gc_content %>%
  mutate(rep_name = gsub("_val_[12]$","",name),
         read = factor(read)) %>% 
  left_join(select(tb_reps,rep_name,cell_line,epitope,rep),by="rep_name") %>%
  mutate(name = paste(cell_line,rep))

p <- ggplot(tb_p,aes(x=gc_content,y=count,color=name,group=name)) +
  facet_grid(rows=vars(epitope),cols=vars(read),scales="free") +
  scale_x_continuous(name = "GC content",labels=function(x) paste0(x,"%")) +
  scale_y_continuous(name = "Reads",labels=prettyNumbers) +
  geom_line() +
  ggtitle("Per-sequence GC content",subtitle="Unfiltered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        axis.ticks.x = element_blank(),
        strip.background = element_blank())
n_col   <- length(unique(tb_p$epitope))
p_height<- 1+n_col*0.75
p_width <- 8
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width,units="in")
```

![](`r p_file`)

## Aligned & filtered {.tabset}
```{r fastqcReadFilt}
fq_flt <- clugPac::read_fastqc(tb_reps$fqc_filt)
```

### Flag summary
```{r fastqcSummaryFilt}
p_file<- "fastqc_flags_filtered.png"
tb_p  <- fq_flt$summary %>%
  mutate(rep_name = str_extract(name,"^[:alnum:]+_[:alnum:]+_[:alnum:]+_[:alnum:]+")) %>%
  left_join(by="rep_name",select(tb_reps,rep_name,cell_line,epitope,cond,rep)) %>%
  mutate(cell_line = factor(cell_line),
         epitope = factor(epitope),
         cond = factor(cond),
         rep = factor(rep),
         flag = factor(flag,levels=c("pass","warn","fail")),
         title = factor(title,levels=select(.,title) %>% unlist %>% unique %>% sort %>% rev))

p <- ggplot(tb_p,aes(x=rep,y=title,fill=flag)) +
  facet_wrap(.~cell_line+epitope+cond,nrow=1) +
  scale_x_discrete(name="Replicates") +
  scale_fill_manual(values=c(pass="lightgreen",
                             warn="orange",
                             fail="firebrick")) +
  geom_tile(color="black") +
  ggtitle("Filtered reads") +
  theme(plot.title = element_text(size=7),
        plot.background= element_rect(fill="white",color=NA),
        panel.background = element_blank(),
        axis.text = element_text(size=4),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        strip.text = element_text(size=5),
        strip.background = element_blank())
n_col <- tb_p %>% select(cell_line,epitope,cond) %>% distinct %>% nrow
p_height  <- 4
p_width   <- 1+0.7*n_cols
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### FastQ Reads {.tabset}
```{r tableStatsFilt}
tb_stats <- fq_flt$basic_statistics %>%
  as_tibble %>%
  mutate(rep_name = str_extract(name,"^[:alnum:]+_[:alnum:]+_[:alnum:]+_[:alnum:]+"),
         measure = gsub(" ","_",gsub("%","pct_",tolower(measure)))) %>%
  pivot_wider(id_cols = rep_name,
              values_from = value,
              names_from = measure) %>%
  left_join(by="rep_name",select(tb_reps,rep_name,cell_line,epitope,cond,rep)) %>%
  mutate(cell_line = factor(cell_line),
         epitope = factor(epitope),
         cond = factor(cond),
         rep = factor(rep)) %>%
  select(rep_name,cell_line,epitope,cond,rep,total_sequences,total_bases,sequence_length,pct_gc) %>%
  mutate(total_sequences = as.double(total_sequences)) %>%
  arrange(cell_line,epitope,cond) %>%
  mutate(rep_name = factor(rep_name,levels=select(.,rep_name) %>% unlist %>% unique)) %>%
  select(cell_line,epitope,cond,rep,everything())
```

#### Barplot
```{r plotFastqReadsFilt,fig.height=4,fig.width=8}
p_file <- "fastqc_barplot_reads_filtered.png"
p<- ggplot(tb_stats,aes(x=rep_name,y=total_sequences,fill=epitope,label=paste0(prettyNumbers(total_sequences,digs = 1),"\n"))) +
  facet_wrap(.~cell_line + cond,scales="free_x",nrow=1) +
  scale_y_continuous(labels = prettyNumbers,name="Reads",expand=expansion(mult=c(0,0.1))) +
  scale_fill_manual(values=ep_colors) +
  geom_bar(stat='identity',position = "dodge",color='black',linewidth=0.5) +
  geom_text(size=2) +
  ggtitle("FastQ read counts",subtitle= "Filtered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height=unit(0.5,"lines"),
        legend.key.width=unit(0.5,"lines"),
        axis.text.x = element_text(angle=45,hjust=1,vjust=1,size=5),
        axis.ticks.x = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(size=6),
        axis.title.x = element_blank())
n_col <- length(unique(tb_stats$rep_name))
p_height<- 4
p_width <- 1+n_col*0.4
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

#### Table
```{r}
tb_stats %>%
  mutate(total_sequences = prettyNumbers(total_sequences)) %>%
  kable %>%
  kable_styling(full_width=FALSE)
```

### Per-base quality scores
```{r plotPerBaseSequenceQualityFilt,fig.width=8,fig.height=4}
p_file <- "fastqc_pb_sequence_quality_filtered.png"
tb_p <- fq_flt$per_base_sequence_quality %>%
  mutate(name = str_extract(name,"^[:alnum:]+_[:alnum:]+_[:alnum:]+_[:alnum:]+"))

p <- ggplot(tb_p,aes(x=base,y=mean,color=name)) +
  scale_x_continuous(name="Base (bp)",expand=c(0,0),labels=abs) + 
  scale_y_continuous(name="Quality score") +
  geom_line() +
  ggtitle("Per-base quality scores",subtitle= "Filtered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        axis.ticks.x = element_blank(),
        strip.background = element_blank())
p_height  <- 4
p_width   <- 6
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### Per-base sequence content
```{r perBaseSequenceContentFilt}
p_file <- "fastqc_pb_sequence_content_filtered.png"
tb_p <- fq_flt$per_base_sequence_content %>%
  rename(rep_name=name) %>%
  mutate(rep_name = str_extract(rep_name,"^[:alnum:]+_[:alnum:]+_[:alnum:]+_[:alnum:]+")) %>%
  as_tibble %>%
  left_join(select(tb_reps,rep_name,cell_line,epitope,cond,rep),by="rep_name") %>%
  rename(position = base) %>%
  pivot_longer(cols=c(a,c,g,t),names_to = "base",values_to="percent")

p <- ggplot(tb_p,aes(x=position,y=percent,color=rep_name,linetype=base)) +
  facet_grid(rows=vars(epitope)) +
  scale_x_continuous(name="Base",expand=c(0,0),labels=abs) +
  scale_y_continuous(name="Percent",labels = function(x) paste0(x,"%")) +
  geom_line() +
  ggtitle("Per-base sequence content",subtitle="Filtered") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        axis.ticks.x = element_blank(),
        strip.background = element_blank())

n_row <- length(unique(tb_p$epitope))
p_height  <- 1+n_row*1.1
p_width   <- 8
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width)
```

![](`r p_file`)

### Per-sequence GC content
```{r perSequenceGCContentFilt}
p_file <- "fastqc_ps_gc_content_filtered.png"
tb_p  <- fq_flt$per_sequence_gc_content %>%
  rename(rep_name=name) %>%
  mutate(rep_name = str_extract(rep_name,"^[:alnum:]+_[:alnum:]+_[:alnum:]+_[:alnum:]+")) %>%
  left_join(select(tb_reps,rep_name,cell_line,epitope,cond,rep),by="rep_name") %>%
  mutate(name = paste(cell_line,rep))

p <- ggplot(tb_p,aes(x=gc_content,y=count,color=rep_name,group=rep_name)) +
  facet_grid(rows=vars(epitope)) +
  scale_x_continuous(name = "GC content",labels=function(x) paste0(x,"%")) +
  scale_y_continuous(name = "Reads",labels=prettyNumbers) +
  geom_line() +
  ggtitle("Per-sequence GC content",subtitle="Filtered") +
   theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill = NA,color='black'),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color="gray80"),
        legend.title = element_blank(),
        legend.text = element_text(size=5),
        legend.key.height = unit(0.5,"lines"),
        legend.key.width = unit(0.5,"lines"),
        axis.ticks.x = element_blank(),
        strip.background = element_blank())
n_col   <- length(unique(tb_p$epitope))
p_height<- 1+n_col*0.75
p_width <- 8
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width,units="in")
```

![](`r p_file`)

# Alignment stats

Alignment percentages are calculated as **reads successfully mapped to primary or spike genomes / total reads**.

When calculating scores between samples, the ratio of *spike* to *primary* reads can be used to normalize: we assume all samples had an equivalent number of *spike* reads, and thus **any missing *spike* reads indicate missing *primary* reads as well**. For this reason, we can *scale down reads of all samples to match the sample with the lowest ratio*. In other words, **we assume the lowest ratio sample lost reads and so we down-sample all others to match it.**

For instance, if **SampleA** has a ratio of 0.02 and **SampleB** has a ratio of 0.01, each ratio is divided into 0.01 to give factors of 0.5 (**SampleA**) and 1 (**SampleB**). A peak with 100 reads in **SampleA** and 50 reads in **SampleB** would be multiplied by their respective factors to both be 50.
```{r loadSpikes}
p_file  <- "alignment_barplot.png"
tb_alg  <- select(tb_reps,rep_name,spike,spike_file) %>%
  apply(1,function(line_in){
    vals <- fread(line_in[['spike_file']],col.names=c("metric","count")) %>%
      as_tibble %>%
      mutate(rep_name = line_in[["rep_name"]])
    vals$metric[1] <- "primary"
    vals$metric[2] <- "spike"
    return(vals)
  }) %>% do.call(rbind,.)

tb_spk  <- tb_alg %>%
  pivot_wider(id_cols = rep_name,names_from = metric,values_from = count) %>%
  mutate(spike_frac = spike / (primary + spike),
         align_total = primary + spike,
         align_pct = (primary + spike) / (primary + spike + ambiguous + unmapped),
         metric = "spike")
  
type_levs=c(ambiguous="gray",unmapped="pink",spike="purple",primary="darkgreen")

tb_alg <- mutate(tb_alg,metric = factor(metric,levels=names(type_levs)))

p_reads<- ggplot(tb_alg,aes(x=rep_name,y=count,fill=metric)) +
  scale_y_continuous(name="Reads",labels=prettyNumbers,expand=expansion(mult=c(0,0.2))) +
  scale_fill_manual(values=type_levs) +
  geom_bar(stat='identity') +
  geom_text(data=tb_spk,mapping=aes(x=rep_name,y=align_total,label=percent(align_pct,accuracy=1)),vjust=0,size=2) +
  ggtitle("Alignment stats") +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill=NA,color="black"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color='gray75'),
        strip.background = element_blank(),
        axis.text.x = element_text(angle=90,hjust=1,vjust=0.5),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.title = element_blank(),
        legend.key.height=unit(0.5,"lines"),
        legend.key.width=unit(0.5,"lines"))

p_spike<- ggplot(tb_spk,aes(x=rep_name,y=spike_frac,fill=metric,label=round(spike_frac,digits=4))) +
  scale_y_reverse(name="Spike frac.",expand=expansion(mult=c(0.1,0))) +
  scale_fill_manual(values=type_levs) +
  geom_bar(stat='identity') +
  geom_text(vjust=1,size=2) +
  theme(plot.background = element_rect(fill="white",color=NA),
        plot.subtitle = element_text(face="italic"),
        panel.background = element_blank(),
        panel.border = element_rect(fill=NA,color="black"),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.5,color='gray75'),
        strip.background = element_blank(),
        axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        legend.position = "none")

p <- cowplot::plot_grid(p_reads,p_spike,ncol=1,align="v",axis = "lr",rel_heights = c(2,1))
n_col <- tb_alg$rep_name %>% unique %>% length
p_height  <- 7
p_width   <- 1 + n_col * 0.4
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width,units='in')
```

![](`r p_file`)

# Peak calling {.tabset}

For individual samples, peaks are called using the genome-wide median as a background.
```{r peakDetails}
tb_p <- tb_pool %>%
  apply(1,function(line_in){
    npks <- read_peak_file(line_in[['npks']]) %>% select(seqnames,start,end,nlog10q,fc_summit) %>% mutate(type = "narrowPeaks",set="Pooled") 
    bpks <- read_peak_file(line_in[['bpks']]) %>% select(seqnames,start,end,nlog10q,fc_summit) %>% mutate(type = "broadPeaks",set="Pooled")
    rbind(npks,bpks) %>% 
      mutate(width = end-start,name=line_in[['pool_name']],
             cell_line = line_in[["cell_line"]],
             epitope = line_in[["epitope"]],
             cond = line_in[["cond"]])
  }) %>% do.call(rbind,.)

tb_r <- tb_reps %>% #filter(row_number() == 1) -> line_in
  apply(1,function(line_in){
    npks <- read_peak_file(line_in[['npks']]) %>% select(seqnames,start,end,nlog10q,fc_summit) %>% mutate(type = "narrowPeaks",set="Replicates") 
    bpks <- read_peak_file(line_in[['bpks']],name_col="rep_name") %>% select(seqnames,start,end,nlog10q,fc_summit) %>% mutate(type = "broadPeaks",set="Replicates")
    rbind(npks,bpks) %>%
      mutate(width = end-start,name=line_in[['name']],
             cell_line = line_in[["cell_line"]],
             epitope = line_in[["epitope"]],
             cond = line_in[["cond"]],
             name = line_in[["rep_name"]])
  }) %>% do.call(rbind,.)

tb_peaks <- rbind(tb_p,tb_r) %>% as_tibble

tb_tly  <- tb_peaks %>%
  group_by(type,set,name,epitope) %>%
  tally(name="count") %>%
  ungroup
```

## Peak counts {.tabset}
```{r plotPeakCounts}
p_file1<- "peak_counts_pooled.png"
p_file2<- "peak_counts_replicates.png"
p_counts<- tb_tly %>%
  group_split(set) %>%
  setNames(sapply(.,function(x) x$set[1])) %>%
  lapply(function(x) { 
    ggplot(x,aes(x=name,y=count,fill=epitope)) +
      facet_grid(cols=vars(type),rows=vars(set),scales="free") +
      scale_y_continuous(expand=expansion(mult=c(0,0.1)),labels=prettyNumbers,name="Peaks") +
      geom_bar(stat="identity",color='black',linewidth=0.5) +
      theme(plot.background = element_rect(fill="white",color=NA),
            panel.background = element_blank(),
            panel.border = element_rect(fill=NA,color="black"),
            panel.grid.major.x = element_blank(),
            panel.grid.major.y = element_line(linewidth=0.5,color='gray85'),
            strip.background = element_blank(),
            axis.text.x = element_text(angle=45,hjust=1,vjust=1),
            axis.title.x = element_blank(),
            axis.ticks.x = element_blank(),
            legend.title = element_blank(),
            legend.position = 'none')
    })
n_col <- length(unique(tb_tly$name))
p_width <- n_col * 0.5
p_height<- 4
ggsave(p_file1,p_counts$Pooled,"png",dpi=300,height=p_height,width=p_width,units="in")
ggsave(p_file2,p_counts$Replicates,"png",dpi=300,height=p_height,width=p_width,units="in")
```

### Pooled

![](`r p_file1`)

### Replicates

![](`r p_file2`)

## Width
```{r plotPeakStats}
tm_vio  <- theme(
  plot.background = element_rect(fill="white",color=NA),
  panel.background = element_blank(),
  panel.border = element_rect(fill=NA,color="black"),
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_line(linewidth=0.5,color='gray85'),
  strip.background = element_blank(),
  strip.text = element_text(size=6),
  axis.text.x = element_text(angle=45,hjust=1,vjust=1,size=5),
  axis.title.x = element_blank(),
  axis.ticks.x = element_blank(),
  legend.title = element_blank(),
  legend.position = 'none')

n_col <- tb_peaks$name %>% unique %>% length
p_wid <- n_col * 0.6
p_hgt<- 4

p_file1<- "peak_widths.png"
p_width <- ggplot(tb_peaks,aes(x=name,y=width,fill=epitope)) +
  facet_wrap(.~set+type,nrow=1,scales="free") +
  scale_y_log10(name="Width",labels = prettyBP) +
  scale_fill_manual(values=ep_colors) +
  geom_violin(draw_quantiles = 0.5,scale = "width") +
  tm_vio
ggsave(p_file1,p_width,"png",dpi=300,height=p_hgt,width=p_wid,units='in')

p_file2 <- "peak_qvals.png"
p_qvals <- ggplot(tb_peaks,aes(x=name,y=nlog10q,fill=epitope)) +
  facet_wrap(.~set+type,nrow=1,scales="free") +
  scale_y_log10(name="-log10(Q-values)") +
  scale_fill_manual(values=ep_colors) +
  geom_violin(draw_quantiles = 0.5,scale = "width") +
  tm_vio
ggsave(p_file2,p_qvals,"png",dpi=300,height=p_hgt,width=p_wid,units='in')

p_file3 <- "peak_summit_fc.png"
p_sums  <- ggplot(tb_peaks,aes(x=name,y=fc_summit,fill=epitope)) +
  facet_wrap(.~set+type,nrow=1,scales="free") +
  scale_y_log10(name="Summit fold changes",labels=function(x) paste0(x,"x")) +
  scale_fill_manual(values=ep_colors) +
  geom_violin(draw_quantiles = 0.5,scale = "width") +
  tm_vio
ggsave(p_file3,p_sums,"png",dpi=300,height=p_hgt,width=p_wid,units='in')
```

![](`r p_file1`)

## Q-values

![](`r p_file2`)

## Summit fold changes

![](`r p_file3`)

## FRiP
```{r plotFRiP}
p_file<- "frip_barplot.png"
tb_p  <- select(tb_reps,rep_name,npks_FRiP) %>%
  apply(1,function(line_in){
    fread(line_in[['npks_FRiP']]) %>%
      mutate(rep_name = line_in[['rep_name']])
  }) %>% do.call(rbind,.) %>%
  left_join(select(tb_reps,rep_name,cell_line,epitope,cond,pool_name),by="rep_name") %>%
  mutate(in_peaks = ifelse(is.na(in_peaks),0,in_peaks),
         pool_name = ifelse(is.na(pool_name),"background",pool_name))

p <- ggplot(tb_p,aes(x=rep_name,y=frip,label=percent(frip,accuracy=0.001))) +
  facet_wrap(.~pool_name,nrow=1,scales="free_x") +
  scale_y_continuous(name="FRiP",expand=expansion(mult=c(0,0.1))) +
  geom_bar(stat="identity") +
  geom_text(size=1.5,vjust=0,hjust=0,angle=45) +
  theme(plot.background = element_rect(fill="white",color=NA),
        panel.background = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_line(linewidth=0.25,color="gray80"),
        panel.border = element_rect(fill=NA,color="black",linewidth=0.25),
        strip.background = element_blank(),
        strip.text = element_text(size=5),
        axis.text.x = element_text(angle=45,hjust=1,vjust=1,size=4),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank())
if(!any(is.na(tb_p$frip))){
  p <- resize_facets(p)
}
n_col <- tb_p$rep_name %>% unique %>% length
p_width <- n_col * 0.5
p_height<- 3
ggsave(p_file,p,"png",dpi=300,height=p_height,width=p_width,units='in')
```

![](`r p_file`)

# Regional plots {.tabset}

```{r generateRegionalPlots}
p_region <- function(gr_window,files_in = tb_files,y_ax_min=10,tb_pks_in= tb_peaks,o_write=FALSE){
  p_file<- as.character(gr_window) %>%
    gsub("[:-]","_",.) %>%
    paste0("_region.png")
  if(!file.exists(p_file) | o_write){
    x_rng <- c(start(gr_window),end(gr_window))
    
    tb_pl   <- select(files_in,pool_name,cell_line,epitope,cond,spike,bdg,bdg_ctrl) %>% distinct
    
    # Treatment signal.
    bdg_rep <- scan_bdg(files_in$bdg_rep,files_in$reps,gr_window) %>%
      left_join(select(files_in,pool_name,cell_line,epitope,cond,reps,spike_rep),by=c("name"="reps")) %>%
      rename(spike = spike_rep) %>%
      mutate(set="pool")
    
    bdg_pl  <- scan_bdg(tb_pl$bdg,tb_pl$pool_name,gr_window) %>%
      left_join(select(tb_pl,cell_line,epitope,cond,spike,pool_name),by=c("name"="pool_name")) %>%
      mutate(pool_name = name,
             set="rep")
  
    tb_bdg  <- rbind(bdg_rep,bdg_pl) %>%
      group_by(pool_name) %>%
      mutate(weight = min(spike) / spike) %>%
      ungroup %>%
      mutate(xmid = (start+end)/2,
             score_adj = score * weight) %>%
      mutate(xmid = case_when(xmid < x_rng[1] ~ x_rng[1],
                              xmid > x_rng[2] ~ x_rng[2],
                              TRUE ~ xmid))
    
    bdg_ctrl<- scan_bdg(files_in$bdg_ctrl,files_in$reps,gr_window) %>%
      left_join(select(files_in,pool_name,cell_line,epitope,cond,reps,spike_rep),by=c("name"="reps")) %>%
      rename(spike = spike_rep) %>%
      mutate(set="pool",
             epitope = params$ctrl_epitope,
             xmid = (start+end)/2) %>%
      group_by(pool_name) %>%
      mutate(weight = min(spike)/spike,
             score = -score,
             score_adj = score * weight) %>%
      ungroup %>%
      mutate(xmid = case_when(xmid < x_rng[1]~x_rng[1],
                              xmid > x_rng[2]~x_rng[2],
                              TRUE ~ xmid))
    
    tb_scales <- tb_bdg %>%
      group_by(pool_name) %>%
      summarize(ymax = 1.1*max(score),.groups='drop') %>%
      mutate(xmin=x_rng[1],
             xmax=x_rng[2],
             ymax = ifelse(ymax < y_ax_min,y_ax_min,ymax)) %>%
      left_join(bdg_ctrl %>%
                  group_by(pool_name) %>%
                  summarize(ymin = min(score),.groups='drop'),by="pool_name")
    
    p <- ggplot(tb_bdg,aes(x=xmid,ymin=0,ymax=score_adj,y=score_adj,fill=epitope,color=epitope,group=name)) +
      facet_wrap(.~pool_name,ncol=1,strip.position = "right") +
      scale_x_continuous(name=grange_desc(gr_window),expand=c(0,0),limits=x_rng,labels=prettyBP) +
      scale_y_continuous(name="Pileup",expand=c(0,0),labels=function(x) ifelse(x<=0,"",x)) +
      scale_color_manual(name="Epitope",values=ep_colors) +
      scale_fill_manual(name="Epitope",values=ep_colors) +
      geom_ribbon(data=bdg_ctrl) +
      geom_ribbon(data=filter(tb_bdg,set == "pool"),mapping=aes(ymax=score),alpha=0.3) +
      geom_ribbon(data=filter(tb_bdg,set == "pool"),alpha=0.8) +
      geom_line(data=filter(tb_bdg,set=="rep"),color='black') +
      geom_rect(data=tb_scales,mapping=aes(xmin=xmin,xmax=xmax,ymin=ymin,ymax=ymax),inherit.aes=FALSE,fill=NA,color=NA) +
      geom_hline(yintercept=0,color="black",linewidth=0.25) +
      theme(plot.background = element_rect(fill="white",color=NA),
            plot.margin = unit(c(0,0.5,0.5,0.5),"lines"),
            panel.background = element_blank(),
            panel.grid.major.x = element_line(linewidth=0.5,color="gray80",linetype="dotted"),
            panel.grid.major.y = element_blank(),
            panel.border = element_rect(fill=NA,color="black",linewidth=0.5),
            panel.spacing.y = unit(0,"lines"),
            strip.background = element_blank(),
            strip.text.y.right = element_text(angle=0,hjust=0,size=6),
            legend.title = element_blank(),
            legend.text = element_text(size=6),
            axis.text = element_text(size=5),
            axis.title = element_text(size=6))
  
    tb_pks <- tb_pks_in %>%
      makeGRangesFromDataFrame(keep.extra.columns = TRUE) %>%
      subset_and_trim_gr(gr_window) %>%
      as_tibble %>%
      mutate(xmid = (start+end)/2) %>%
      left_join(tb_scales,by=c("name"="pool_name")) %>%
      mutate(y_trac = 0.05*(ymax-ymin),
             y1 = ifelse(type == "broadPeaks",ymax - y_trac,ymax - 2*y_trac),
             y2 = y1 + y_trac,
             y1 = ifelse(set == "Replicates",ymin,y1),
             y2 = ifelse(set == "Replicates",ymax,y2)) %>%
      dplyr::rename(pool_name = name)
    if(nrow(tb_pks)>0){
      p <- p +
        new_scale_fill() +
        geom_rect(tb_pks,mapping=aes(xmin=start,xmax=end,ymin=y1,ymax=y2,fill=type,alpha=set),inherit.aes=FALSE) +
        scale_fill_manual(values=c("broadPeaks"="orange","narrowPeaks"="darkgreen")) +
        scale_alpha_manual(values=c("Pooled"=1,"Replicates"=0.5)) +
        guides(alpha="none")
    }
    
    n_row <- length(unique(tb_bdg$pool_name))
    p_height  <- 3 + (0.6*n_row)
    p_width   <- 9
    p_gns <- plot_genes_from_gtf(gr_window,gn_gtf)
    p_out <- cowplot::plot_grid(p_gns,p,ncol=1,align="v",axis="lr",rel_heights = c(1,n_row+1))
    ggsave(p_file,p_out,"png",dpi=300,height=p_height,width=p_width,units='in')
  }
  return(p_file)
}

peak_count  <- 5
chrom_cutoff<- 5E6
ptile_cutoff<- 0.95
min_width   <- 20000

tb_files <- tb_pool %>%
  select(-reps_bkg) %>%
  mutate(reps = str_split(reps,pattern=":")) %>%
  unnest(reps) %>%
  left_join(select(tb_reps,rep_name,npks,bpks,bdg,spike) %>% rename(npks_rep=npks,bpks_rep=bpks,bdg_rep=bdg,spike_rep=spike),by=c("reps"="rep_name")) %>%
  select(-genome,-genome_spike)

prev_peaks  <- tb_peaks %>%
  filter(epitope != params$ctrl_epitope,
         set == "Pooled",
         start > chrom_cutoff,
         end < get_seqsizes()[as.character(seqnames)]-chrom_cutoff) %>%
  group_by(cell_line,epitope,cond) %>%
  mutate(ol_q = quantile(nlog10q,ptile_cutoff),
         ol_f = quantile(fc_summit,ptile_cutoff)) %>%
  filter(nlog10q < ol_q,fc_summit < ol_f) %>%
  arrange(desc(ol_q),desc(ol_f)) %>%
  mutate(idx = row_number()) %>%
  ungroup %>%
  filter(idx <= peak_count) %>%
  rowwise %>%
  mutate(center = (start+end)*0.5) %>%
  mutate(width = ifelse(width < min_width,min_width,width*1.5)) %>%
  mutate(start=as.integer(center-width/2),
         end = as.integer(center+width/2)) %>%
  mutate(p_file = {
    suppressWarnings(
      p_region(GRanges(seqnames,IRanges(start,end)),
               files_in = tb_files,
                         y_ax_min = 10,
                         tb_pks_in = tb_peaks,
                         o_write=FALSE)) 
  }) %>%
  ungroup
```

Preview up to `r peak_count` peaks from each combination of cell line, epitope (excluding `r params$ctrl_epitope`), and condition. Exclude peaks with summit fold changes or Q-values that are in the `r paste0(ptile_cutoff*100,"th")`percentile or that fall within `r prettyBP(chrom_cutoff)` of a chromosome end.
```{r,results='asis'}
prev_peaks %>%
  group_split(name) %>%
  lapply(function(tb_in){
    p_nm <- tb_in$name[1]
    cat("\n\n##",p_nm,"{.tabset}")
    apply(tb_in,1,function(line_in){
      cat("\n\n###",line_in[["idx"]])
      cat("\n\n![](",line_in[["p_file"]],")")
    }) %>% invisible
  }) %>% invisible
```